\LARGE \bf Object Detection-Based Behaviour using YOLO on Thymio

### 2018-05-31 paper/paper.tex
Added things to paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
The ability to classify in booth space and domain objects is encoded in an enormous variety of species on the planet. Recently, deep learning approaches have been developed to make machines able to mimic the same task with interesting results. With this paper, we propose a minimal architecture to archive the same goal using a two wheels robots, the Thymio, with a mounted frontal camera in order to act based on the object detected in the surrounding. 
\end{abstract}
\section{Introduction}
Finding objects in space by identifying their identity and their coordinates is a basic task that almost each animal is able to accomplish by feeding the inputs from their eyes to the brain. The ability to solve this problem is extremely important in robotics, where a machine needs to act accordingly based on its surrounding. With our architecture, only the raw data from the camera are used as input to an Object Detection model and the decision are based directly on the prediction, without the need of any other sensor.

@@

\section{Architecture}
Our architecture is composed by:
\begin{enumerate}
	\item A robot with a mounted camera and an on-board computer with a running ROS node
	\item A web server running the Object Detection model
	\item A ROS node running on a local machine
\end{enumerate}
As a robot, we used the \emph{MightyThymio} \cite{guzzi2018eaai}, which is a robot developed on top of the Thymio, a small mass-produced mobile robot usually used in primary and secondary education. The MightyThymio has a powerful Odroid C1 on board, a 1GB quad-core ARM Linux machine, with a HD camera mounted on top. The authors also implemented a ROS node to communicate with it and open-sourced the code.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{YOLO: REAL-TIME OBJECT DETECTION}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
The ability to classify in booth space and domain objects is encoded in an enormous variety of species on the planet. Recently, deep learning approaches have been developed to make machines able to mimic the same task with interesting results. With this paper, we propose a minimal architecture to archive the same goal using a two wheels robots, the Thymio, with a mounted frontal camera in order to act based on the object detected in the surrounding. 
\end{abstract}

\section{Introduction}

Finding objects in space by identifying their identity and their coordinates is a basic task that almost each animal is able to accomplish by feeding the inputs from their eyes to the brain. The ability to solve this problem is extremely important in robotics, where a machine needs to act accordingly based on its surrounding. With our architecture, only the raw data from the camera are used as input to an Object Detection model and the decision are based directly on the prediction, without the need of any other sensor.

@@

\section{Architecture overview}

Our architecture is composed by:
\begin{enumerate}
	\item A robot with a mounted camera and an on-board computer with a running ROS node;
	\item A web server running the Object Detection model;
	\item A ROS node running on a local machine.
\end{enumerate}
As a robot, we used the \emph{MightyThymio} \cite{guzzi2018eaai}, which is a robot developed on top of the Thymio, a small mass-produced mobile robot usually used in primary and secondary education. The MightyThymio has a powerful Odroid C1 on board, a 1GB quad-core ARM Linux machine, with a HD camera mounted on top. The authors also implemented a ROS node to communicate with it and open-sourced the code.

\subsection{Configuration}

In our project, the MightyThymio has the same configuration proposed in \cite{guzzi2018eaai}. On the on-board computer of the robot there is a running ROS node that can publish and subscribe in order to communicate with its sensors: it can have information from the proximity sensors to avoid hitting obstacles, it can take images from the mounted camera, it can use the leds to indicate an object or a direction, and more. On the local machine there is another running ROS node that specifies the behaviour of the MightyThymio based on the presence of specific objects around him.

%Subscribe thyme event of camera, from whom compressed images, encoded in strings, then we send to the server, the server decode the compressed images and send prediction. After prediction, if class is target, for example person, the server send the person and bounding box. If the timeo see the person, it moves verso the person keeping her in the centre. So if the person moves, the timeo moves to keep the bounding box in the centre of the camera. So using only the image we can tell timeo to follow a target, without knowing the position of target or of thimeo.
%The rod node is a module that can be put where you want.

\subsection{ROS: Robot Operating System}
ROS is a robotics middleware that provides libraries and tools to help software developers create robot applications by supplying hardware abstraction, device drivers, message-passing, and more. One main concepts in ROS is the node, which is included in the level of Computation Graph, the peer-to-peer network of ROS processes that are processing data together. Nodes are processes that perform computation; a robot control system usually comprises many nodes, that act as modules.

\subsection{YOLO: Real-Time Object Detection}

@@

\section{Code}

\section{Server}
